I am pleased to present the Workshop Proceedings of the Twenty-Third International Conference on Case-Based Reasoning (ICCBR-15), held on September 28\textsuperscript{th} - 30\textsuperscript{th} in Frankfurt, Germany. This year brings a mix of both new and established workshops promising to heighten engagement and innovation in CBR, including a new installment of the long-running \textit{CBR in the Health Sciences} workshop, a second year of the successful \textit{Case-Based Agents} workshop, and a new workshop on \textit{Experience and Creativity}. This year also features proceedings from the eighth \textit{Computer Cooking Contest} as well as the seventh \textit{Doctoral Consortium} -- an event in which doctoral students present and receive important feedback on their dissertation research. 

I would like to thank all who contributed to the success of this workshop program, especially the authors and presenters who provided the research insights comprising the essential substance of the workshops. I would also like to thank all of the program committee members for their contributions leading to high-quality submissions, and I'd especially like to thank the workshop organizers for their hard work over the past year developing a compelling collection of workshop programs. 

My special thanks go to the program chairs, Mirjam Minor and 
Eyke \\* H\"ullermeier, the local chairs, Eric K\"ubler and Jenny Quasten, and the publicity chair, Pascal Reuss, for their continuous support, efforts in planning the event, and assistance with producing the proceedings. I'd also like to thank David Leake for his support and assistance. 

I hope that authors and other participants enjoy and are invigorated by this year's workshop program and also find valuable resources in these proceedings for furthering their research. I look forward to a fruitful exchange of ideas in Frankfurt.

